Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-04-26 hb.tex
typo

It is worth clarifying here what axioms and lemmas are by looking at the
two distinct use cases for a hierarchy: 1) develop the abstract theory of some
structure; 2) apply the abstract theory on some concrete example.
In the first case
all the axioms of the structure are (assumed to be) theorems so the distinction
between axiom and theorem does not matter. This is what happens
in the proof of \coq{addNr} by taking \coq{R} to be of type
\coq{AbelianGroup.type} as an assumption.
In the second case,
in order to show Coq that a data type and some operations for a structure,
one must pick the axioms of the structure an prove them for that specific
type and operations. For example the \coq{Ring_of_Monoid.Build} \phantterm{}
is used at page~\pageref{demo:theory:z:ring:axioms} to package the set
of proofs that make \coq{Z} a ring (proviso \coq{Z} is already a monoid).

>>>>

It is worth clarifying here what axioms and lemmas are by looking at the
two distinct use cases for a hierarchy: 1) develop the abstract theory of some
structure; 2) apply the abstract theory on some concrete example.
In the first case
all the axioms of the structure are (assumed to be) theorems so the distinction
between axiom and theorem does not matter. This is what happens
in the proof of \coq{addNr} by taking \coq{R} to be of type
\coq{AbelianGroup.type} as an assumption.
In the second case,
in order to show Coq that a data type and some operations forms a structure,
one must pick the axioms of the structure an prove them for that specific
type and operations. For example the \coq{Ring_of_Monoid.Build} \phantterm{}
is used at page~\pageref{demo:theory:z:ring:axioms} to package the set
of proofs that make \coq{Z} a ring (proviso \coq{Z} is already a monoid).
